|

### 2019-12-03 article/letter.Rmd
v2 memo

We have worked specially hard to clarify the connection between information provision and mobilisation, a point emphasised by both the editor and the reviewer. Our efforts in that regard include, first, a new section in the SI Appendix with a detailed description of _Tá de Pé_'s functionalities and the associated Facebook campaigns. We explain the precautions we have taken to ensure that the

Related, we have included a discussion regarding app usage as suggested by the reviewer.

>>>>

We have worked specially hard to clarify the connection between information provision and mobilisation, a point emphasised by both the editor and the reviewer. Our efforts in that regard include, first, a new section in the SI Appendix with a detailed description of _Tá de Pé_'s functionalities and the associated Facebook campaigns. We explain the precautions we have taken to ensure that the we correctly identify the effect of the TDP app on school outcomes. Second, we provide a thorough discussion of our additional data sources. More specifically, we show how the Brazilian Ministry of Education collects and publicises their data and indicate how our experiment uses that information to evaluate the robustness of our findings. We believe the new sections help give the results a clearer interpretation and strenghten our main arguments.

Related, we have included a discussion regarding app usage as suggested by the reviewer. We have included information provided by Google Analytics not only on app downloads but also on app usage, which addresses another important concern raised by the reviewer. The data show that the app usage was significant, yet it was not enough to trigger any responses from local governments.

Lastly, we have rewritten some parts of the main text to highlight that our experiment hinges on participation only, and that the effect of mobilisation and pressure on school construction outcomes require further analyses.We believe our paper now reflects our results more accurately.
